Thesis Title

### 2022-03-20 chapters/paper1.tex
Updates from Overleaf

>>>>

\subsection{Characterisation of mobile genetic elements}

Two different approaches, i.e. CLC Genomics Workbench and Bowtie2 were used to identify plasmids present in the sequence data. 
Both approaches used mapping of sequences against the same plasmid database. 
Since some plasmids present in the database are very similar and sequence reads may be mapped to more than one plasmid, we used the pATLAS tool, which provides an overview of the nodes (representing plasmid sequences) and links between plasmids (which connect similar plasmids), to enable the visualisation of the plasmids identified (Figure \ref{}). 
A colour gradient indicates the sequence coverage of the plasmids. 
In most cases, the same plasmids were identified by both approaches, with some small differences in sequence coverage. 
When comparing the plasmids identified in the SMg dataset versus the WGS data, most of the plasmids were also detected in the isolates (an example is shown in Figure \ref{}). 
However, some plasmids were not identified in any of the isolated bacteria and were probably residing in low-abundant species.
